Competing Bandits

### 2017-12-03 Writeup/writeup.tex
tweaks to regret + epsilon probs

In this project we mainly look at the following sequence of actions:
\begin{enumerate}
\item Two principals compete against each other for agents and each can only get reward if an agent picks them over the other.
\item At each $t = 1,...,T$, a single agent enters (and lives only for one period) and selects a principal based on some belief they have about the expected payoff from picking each principal.
\end{enumerate}

@@

Then, we implemented the following four behavioral algorithms that describe the decision rule of the agent given the reputation score:
\begin{enumerate}
\item HardMax where the agent chooses the firm with a larger score, breaking ties uniformly
\item HardMaxRandom: Each agent uses HardMax with probability $1 - \epsilon$ and an action chosen uniformly at random with probability $\epsilon$
\item SoftMax: Each firm is chosen with probability $e^{\alpha score}$ for some given $\alpha$
\item SoftMaxRandom: Each agent uses SoftMax with probability $1 - \epsilon$ and an action chosen uniformly at random with probability $\epsilon$
\end{enumerate}

In the simulations we maintained the assumption in the paper that the principals commit to a learning algorithm in the first period and thus we implemented standard bandit learning algorithms for the principals. In general, we were interested in thinking about the differences that would arise when the principals were running greedy algorithms, non-adaptive exploration algorithms, or adaptive exploration algorithms.

@@

[Insert some plots]

[Insert some analysis]

\section*{Experiment 2 - Which Algorithm Wins?}
This experiment mainly looked at what happens if we fix the priors of the principals and the agents to be identical at the beginning of the simulation.

@@

\section*{Experiment 3 - Tuning SoftMax}
This experiment mainly looked at what happens if we do a grid search over alpha parameters in tuning SoftMax.

@@

\section*{Experiment 5 - Warm Start and HardMax}
What is the effect of a ``warm start" on the performance of HardMax? Our simulations show that with HardMax the initial rounds matter a lot in a particular simulation and whoever wins in the first few rounds takes the entire market. We explore if having a warm start makes it so that the market is more evenly split.

[results]

>>>>

In this project we mainly look at the following sequence of actions:
\begin{enumerate}
\item Two principals compete against each other for agents and each can only get reward if an agent picks them over the other. Before the beginning of the game, each principal selects a bandit algorithm to use. 
\item At each $t = 1,...,T$, a single agent enters (and lives only for one period) and selects a principal based on some belief they have about the expected payoff from picking each principal.
\item The chosen principal runs its bandit algorithm to select an arm. The reward generated by the arm is given to the agent. 
\end{enumerate}

@@

Then, we implemented the following four behavioral algorithms that describe the decision rule of the agent given the reputation score:
\begin{enumerate}
\item HardMax where the agent chooses the firm with a larger score, breaking ties uniformly
\item HardMaxRandom: Each agent uses HardMax with probability $1 - \epsilon$, and chooses between the principals uniformly at random with probability $\epsilon$
\item SoftMax: Each firm is chosen with probability $e^{\alpha score}$ for some given $\alpha$
\item SoftMaxRandom: Each agent uses SoftMax with probability $1 - \epsilon$ and chooses between the principals uniformly at random with probability $\epsilon$ %can we remove this? SoftMaxWithRandom doesn't exist in the paper, and I think it's pointless because SoftMax already gives a baseline probability to each principal to be chosen
\item Uniform: Each agent chooses between the two principals uniformly at random
\end{enumerate}

In the simulations we maintained the assumption in the paper that the principals commit to a learning algorithm in the first period and thus we implemented standard bandit learning algorithms for the principals. In general, we were interested in thinking about the differences that would arise when the principals were running greedy algorithms, non-adaptive exploration algorithms, or adaptive exploration algorithms. Bandit algorithms that we implemented include:
\begin{enumerate}
\item ExploreThenExploit
\item StaticGreedy
\item DynamicGreedy
\item DynamicEpsilonGreedy
\item ThompsonSampling
\item UCB
\end{enumerate}

@@

\begin{center}
Agent: HardMax \\Principals: Thompson Sampling vs Thompson Sampling
 \begin{tabular}{||c c c c c||} 
 \hline
 Memory Size & Principal 1 MS & Principal 2 MS & Principal 1 Avg Regret & Principal 2 Avg Regret  \\ [0.5ex] 
 \hline\hline
 1 & 0.498 & 0.502 & 0.021 & 0.021 \\ 
 \hline
 5 & 0.5219 & 0.478 &  0.119 &  0.132 \\
 \hline
 10 & 0.407 & 0.593 & 0.165  & 0.113 \\
 \hline
 50 & 0.420 & 0.580 & 0.168 & 0.131 \\
 \hline
 100 & 0.460 & 0.540 & 0.161 & 0.160 \\ [1ex] 
 \hline
\end{tabular}

\vspace{0.75cm}
Agent: HardMax \\Principals: Thompson Sampling vs Dynamic $\epsilon$-Greedy
 \begin{tabular}{||c c c c c||} 
 \hline
 Memory Size & Thompson Sampling MS & Principal 2 MS & Principal 1 Avg Regret & Principal 2 Avg Regret  \\ [0.5ex] 
 \hline\hline
 1 & 0.508 & 0.491 & 0.020 & 0.029 \\ 
 \hline
 5 & 0.464 & 0.536 &  0.128 &  0.109 \\
 \hline
 10 & 0.248 & 0.751 & 0.218  & 0.062 \\
 \hline
 50 & 0.160 & 0.839 & 0.259 & 0.0338 \\
 \hline
 100 & 0.161192 & 0.834 & n/a & n/a \\ [1ex] 
 \hline
\end{tabular}
\end{center}
For the case of 100, there were many cases when the principal was never chosen!

\section*{Experiment 2 - Which Algorithm Wins?}
This experiment mainly looked at what happens if we fix the priors of the principals to be identical over the arms and the agents to be identical over the principals at the beginning of the simulation.

@@

\section*{Experiment 3 - Tuning SoftMax} % might want to put this one at the top
This experiment mainly looked at what happens if we do a grid search over alpha parameters in tuning SoftMax. % you have to tune both alpha and epsilon for SoftMax

@@

We simulate this in the following scenario. We set $K = 10$

\section*{Experiment 5 - Warm Start and HardMax}
What is the effect of a ``warm start" on the performance of HardMax? Our simulations show that with HardMax the initial rounds matter a lot in a particular simulation and whoever wins in the first few rounds takes the entire market. We explore if having a warm start makes it so that the market is more evenly split in a given simulation.\\

We experimented with giving a warm start of 0, 5, 25, 50, and 100 observations to each principal. We ran the following competing algorithms: UCB vs UCB, UCB vs DynamicGreedy, StaticGreedy vs UCB and observed little effect. Regardless of the algorithm that was played or the number of free observations we gave to the principals, the sequence of simulations lead to market shares in each simulation looking roughly the same. Namely, in a given simulation one of the principals would take the entire market but since the principals had the same priors over the arms and the agents had the same priors over the principals, it was random who would take the entire market. Thus, it seems that free observations for the principal do not impact the resulting market share.
